\documentclass{muratcan_cv}

\setname{\Huge{Mukul Joshi}}{}
\setaddress{Udaipur/Rajasthan}
\setmobile{7073773473}
\setmail{shmj179@gmail.com}
\setcodewars{https://www.codewars.com/users/vim1729}
\setgithubaccount{https://github.com/mukul1729?tab=repositories} %you can play with color of the template (red is also nice..)
\setvimeo{https://vimeo.com/566776779}
\setthemecolor{brown}

\begin{document}
%Set variables
%You can add sections, texts, explanations just by copying the style below. Replace the dummy texts "\lipsum[1][x-x]\par" with actual texts.
%Create header
\headerview
\vspace{1ex}
%Sections
%
%
%Education
\section{Education} 
	\datedexperience{College Of Technology and Engineering,Udaipur}{2017-2021} 
	\newcommand{\college}{
		B.Tech in Electronics and Communication 
		\cpshalf 62.1\% \cpshalf M.P.U.A.T}
	\createbullets{\college}

    \datedexperience{Central Academy Senior Secondary School,Udaipur}{2014-2016} 
	\newcommand{\schoolone}{
		12th Examination 
		\cpshalf 84\%       Central Board of Secondary Education
	}
	\newcommand{\schooltwo}{
		10th Examination 
		\cpshalf 7.6 CGPA Central Board of Secondary Education
	}
	\newcommand{\school}{\schoolone,\schooltwo}
	\createbullets{\school}
     
%

\section{Skills}
    %
    \newcommand{\skillone}{\createskill{Programming
	Languages}{\textbf{\emph{Experienced:}} \ \  Python \cpshalf C \ \
	\textbf{\emph{Familiar:}} \ \  C++ \cpshalf Java \cpshalf Dlang \cpshalf
	SQL \cpshalf Bash \cpshalf PHP}}
    %
    \newcommand{\skilltwo}{\createskill{Software Development}{Programming Paradigms
	\cpshalf GIT \cpshalf CLI \cpshalf Data Structures and Algorithms }}
    %
    \newcommand{\skillthree}{\createskill{Frameworks \ \& \ Libraries}{Pygame \cpshalf
	Matplotlib \cpshalf Flask \cpshalf Linux \cpshalf Django }}
    %
    \newcommand{\skillfour}{\createskill{Markup Languages}{\LaTeX \cpshalf HTML \cpshalf
	Markdown }}
	\createskills{\skillone, \skilltwo, \skillthree, \skillfour}
% Experience
\section{Projects}
    %
	\datedexperience{Paint Program }{Desktop
	Application,Python,Pygame,Tkinter,Numpy}

    \newcommand{\paintone}{
	Designed a raster graphics editor that allows users to create and edit images
	interactively on a computer screen.
    }
    \newcommand{\painttwo}{
		Flood Fill algorithm is used to implement the Paint Bucket tool. Deque is used to
		implement Tabs functionality.
    }
    \newcommand{\paintthree}{
		Implemented Drawing Tools such as Rectangle, Ellipse, Line, Freehand,
		Paint Bucket, Copy Tool, Eraser.
    }
    \newcommand{\paint}{\paintone, \painttwo, \paintthree}
    \createbullets{\paint}

    \datedexperience{Sorting Visualizer}{Desktop Application,Python,Pygame}
	\newcommand{\sortingone}{
		Visualization of Sorting Algorithms such as Merge Sort, Bubble Sort, Selection Sort, Quicksort, Insertion Sort.
	}
	\newcommand{\sortingtwo}{
		In-Place Quick Sort and In-Place Merge Sort are used 
		 for faster sorting and better memory management.
	}
	\newcommand{\sorting}{\sortingone,\sortingtwo}
	\createbullets{\sorting}


	\datedexperience{Mini Projects}{}
	\newcommand{\minione}{
		Built a Simple Equation solver using Abstract Syntax Trees, which can
		solve simple algebraic equations.
	}
	\newcommand{\minitwo}{
		Designed Terminal Todo list program with functionality of add, delete,
		list, done, report of Todo items.
	}
	\newcommand{\minithree}{
		Designed Sierpinski carpet and Cantor set visualization (Infinite self
		similar patterns) in pygame.
	}
	\newcommand{\mini}{\minione,\minitwo,\minithree}
	\createbullets{\mini}

%
\section{Achievements}
	\newcommand{\achieveone}{
		Top \textbf{2\%} with World Rank of \textbf{6949} at codewars.com and
		solved \textbf{200+} problems on codewars.
		\hspace{7.0mm}
		\href{https://www.codewars.com/users/vim1729}{\underline{\textbf{Codewars
		Profile}}}
	}
	\newcommand{\achievetwo}{
		Top \textbf{1\%} with 23k points at interviewbit.com and solved \textbf{100+} 
		problems on interviewbit.
		\hspace{7mm}
				\href{https://www.interviewbit.com/profile/vim1729}{\underline{\textbf{InterviewBit Profile}}}

	}
	\newcommand{\achievethree}{
		Scored \textbf{96\%} in coding round of  CoCubes assesment. Top \textbf{97} percentile in
		India. 
	}
	\newcommand{\achievefour}{
		\textbf{1059} contest rating on codeforces.com and solved \textbf{380+} problems on
		codeforces.
		\hspace{17.4mm}
				\href{https://codeforces.com/profile/vim1729}{\underline{\textbf{Codeforces
				Profile}}}
			}

	\newcommand{\achievefive}{
		Attained \textbf{Five stars} ,Golden Badge for Python Programming on HackerRank.
		}

	\newcommand{\achieve}{\achieveone,\achievetwo,\achievefour,\achievethree,\achievefive}
	\createbullets{\achieve}

\section{Certificates \& Courses}
    \newcommand{\extraone}{
		\textbf{Problem Solving Ability Test} consisted of Sorting,
		Searching, Dictionary \& Array Problems by \textbf{HackerRank}.
		\hspace{0.0mm}
				\href{https://www.hackerrank.com/certificates/359641cab60b}
				{\underline{\textbf{LINK}}}
			}
    \newcommand{\extratwo}{
		\textbf{Python Assessment} consisted of Collections, Iteration, Modularity,
		Objects and Classes by \textbf{HackerRank}
		\hspace{5.0mm}
				\href{https://www.hackerrank.com/certificates/50636fc435a0}
				{\underline{\textbf{LINK}}}
			}
    \newcommand{\extrathree}{
		\textbf{Data Structures and Algorithms in Python} by the instructor,
		Holczer Balazs through \textbf{Udemy}.
		\hspace{20.0mm}
				\href{https://www.udemy.com/certificate/UC-10569178-738a-4669-8ba0-ae1d6a3934e7/}
				{\underline{\textbf{LINK}}}
			}
    \newcommand{\extrafour}{
		\textbf{Java Assessment} consisted of Strings, Classes, Inheritance,
		Exception Handling by \textbf{HackerRank}.
		\hspace{15.0mm}
				\href{https://www.hackerrank.com/certificates/8c215bd9fde1}
				{\underline{\textbf{LINK}}}
			}
	\newcommand{\extrafive}{
		\textbf{Introduction to Algorithms and Data Structures} 6.006 through MIT OPENCOURSEWARE.
	}
    \newcommand{\listofextras}{\extraone, \extratwo, \extrafour, \extrathree,
	\extrafive}
    \createbullets{\listofextras}
\section{EXPERIENCE}
	\datedexperience{Codewars}{2020-Present}
	\explanation{Problem Setter}
	    \explanationdetail{\coloredbullet\ %
		Authored several Problems on Codewars ranging from Hashing to Divide
		and Conquer.
     }
	    \explanationdetail{\coloredbullet\ %
		Those problems were solved by a total of 206 Users and earned 31 Stars.
		}
	
\createfootnote
\end{document}
